Uncertainty on the galaxy-halo connection for Lyman-$\alpha$ emitters at $z=3.1$

### 2016-03-23 paper/ms.tex
little typo

\subsection{Observational constraints}
\label{subsec:obs}
\citet{Bielby16} used narrow band imaging to detect 643 LAE candidates
at $z\sim 3$  with equivalent widths of $\gtrsim$65\AA\ and a flux limit
of $2\times10^{17}{\rm erg/cm^2/s}$ ($L\sim 7\times10^{42}{\rm erg/s} $). 
Using spectroscopy they found a 22\% contamination fraction.
Their observations cover 5 (out of 9) independent and co-spatial fields of the VLT LBG Redshift Survey (VLRS). 
The  total observed  area corresponds to 1.07$\rm deg^2$ that translates to
$\sim$80$^2\hMpc^2$ in a comoving scale. \citet{Bielby16} used the
NB497  narrow-band filter whose 77\AA\ FWHM and 154\AA FWTM correspond to a total observational depth of 44\hMpc\  and 82\hMpc\ comoving, respectively.

>>>>

\subsection{Observational constraints}
\label{subsec:obs}
\citet{Bielby16} used narrow band imaging to detect 643 LAE candidates
at $z\sim 3$  with equivalent widths of $\gtrsim$65\AA\ and a flux limit
of $2\times10^{17}{\rm erg/cm^2/s}$ ($L\sim 7\times10^{42}{\rm erg/s} $). 
Using spectroscopy they found a 22\% contamination fraction.
Their observations cover 5 (out of 9) independent and co-spatial fields of the VLT LBG Redshift Survey (VLRS). 
The  total observed  area corresponds to 1.07$\rm deg^2$ that translates to
$\sim$80$^2\hMpc^2$ in a comoving scale. \citet{Bielby16} used the
NB497  narrow-band filter whose 77\AA\ FWHM and 154\AA\ FWTM correspond to a total observational depth of 44\hMpc\  and 82\hMpc\ comoving, respectively.
